paper1_results_figs_slimmed_50_rr

### 2016-10-26 inst/documents/paper1_results_figs_slimmed_50_rr.Rmd
tweaking pap1 figs

# Fig2 replicating Curtis
```{r Fig2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=3.5, fig.width=6, fig.keep='last'}

>>>>

![curtis fig1](pap1_curtis1.png)

# Fig2 replicating Curtis, and now adding in copies of Curtis plots
```{r Fig2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=8.5, fig.width=6, fig.keep='last'}

  #set layout for 4 plots, A&C Curtis, B&D new ones
  layout(matrix(1:4,2,2,byrow=FALSE))

  #add in images of curtis plots here
  #to get into the layout I need to do from R
  #may be ugly
  par(mar=c(0.4,2.9,0,0.4)) #bltr default is c(5, 4, 4, 2)

  image(system.file("documents","pap1_curtis1.png", package="resistance"))

  image(system.file("documents","pap1_curtis2.png", package="resistance"))

  par(mar=c(0.4,2.9,0,0.4)) #bltr default is c(5, 4, 4, 2)

  #2B
  calibration <- 1011
  input <- createInputMatrix( params.csv=FALSE, calibration=calibration )
  listOut <- runModel2( input, calibration )
  #we submitted the LD one but should have done the Fig1
  #plotcurtis_ld( listOut$results[[1]], listOut$results[[2]], 1, 4 )
  plotcurtis_f1( listOut$results[[1]], listOut$results[[2]], 1, 2 )
  #side=1=bottom, 2=left, 3=top, 4=right, adj=0 left justify, lines move outwards
  mtext('B)',side=3, adj=0, line=1)

  #2D
  calibration <- 1012
  input <- createInputMatrix( params.csv=FALSE, calibration=calibration )
  listOut <- runModel2( input, calibration )  
  plotcurtis_f2( listOut$results[[3]], listOut$results[[1]], listOut$results[[2]], 1, 2, 3 )
  #side=1=bottom, 2=left, 3=top, 4=right, adj=0 left justify, lines move outwards
  mtext('D)',side=3, adj=0, line=1)

```{r Fig2_justNew, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=3.5, fig.width=6, fig.keep='last'}
